---
title: "Welcome to {Your} R Collaborative"
subtitle: "Work in progress"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
params:
  collab_short: "Your R Collab"
  collab_long: "Your R Collaborative"
  collab_github: "https://github.com/repo_owner/repo_name"
  coc_link: "https://yourdomain.github.io/coc/"
  collab_email: "your_collab_email@somewhere.com"
  coc_report_link: "https://your_report_link.com"
  collab_slack_faq: "#collab-faq"
  collab_schedule_link: "https://your_schedule_link.com"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# set up key variables for processing later
collab_wiki_link <- glue::glue("{collab_github}/wiki", collab_github = params$collab_github)
```


# Thank YOU!

* You could have been doing anything today...
* But you chose to join us for this event!
* Especially a big thank you to our **mentors**

.center[
```{r thank_image, out.width = "40%"}
knitr::include_graphics("http://bit.ly/momtocat")
```
]

---

# Code of Conduct

The `r params$collab_long` (henceforth referred to as the "`r params$collab_short`") is dedicated to providing a **harrassment-free experience** for participants at our event.  The `r params$collab_short` is an informal, community-led hackathon intended for prefessional networking and collaboration in the R community.

An inclusive space free of harrassment encourages interaction among diverse groups.  We want to **make certain our event is welcoming and encourages participants to be involved** moving forward.

Read more: `r params$coc_link`

---

# Reporting

Several options:

* Message event organizers
* Contact `r params$collab_email`
* Fill out anonymous [report form](`r params$coc_report_link`)
* IF needed, organizers can set up a chat with individual(s) affected
* Let us know if you see things we should be aware of

---

# Event Organizers

**TODO** Add custom R code chunk to loop through organizer avatars and create a row of pictures with their name below.  

---

# Need help?

* __Zoom__ troubleshooting - **TODO add points of contact**
* __Slack__ -  **TODO add points of contact**
    + ``r params$collab_slack_faq`` for questions
* __GitHub__ access - **TODO add points of contact**

---

# Zoom Basics

* Mute/unmute + video/no video
* Chat window
* Screenshare
* Reactions
* Security - please keep the room links private!
    + They will also __change tomorrow__ for security purposes.
    + Be careful of screenshots you take - make sure they don't include meeting ID

---

# Schedule

* Intended mix of sync / async participation
* Visual version + room sign up: [Goole Sheet](`r params$collab_schedule_link`)
* Written version: [Github wiki page](`r collab_wiki_link`)

---

# Schedule - Day 1

**TODO**: Use `googlesheets` to dynamically extract the sheet for the schedule and print via `{DT}`, `{kableExtra}`, or other table printing package

---

# Schedule - Day 2

**TODO**: Use `googlesheets` to dynamically extract the sheet for the schedule and print via `{DT}`, `{kableExtra}`, or other table printing package

---

# Birds of a Feather

* Open time over lunch to discuss a topic that's interesting to you
* If there's something you want to discuss, [sign up](`r params$collab_schedule_link`)!
* Topic ideas:
    + Data visualization
    + Causal inference
    + Reproducibility
    + Communication and reporting
    + Other ideas
    
---

# Questions?

Don't hesitate to ask us about anything!

``r params$collab_slack_faq`` for future Qs
